Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-04 inspiral_svd.tex
Revised abstract
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@742 ccdd05d5-56c1-461a-bf98-85f6876523b4

@@

\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  Département de physique, École Normale Supérieure de Cachan, 61
Avenue du Président Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de Física, Universitat de València, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors offers a unique opportunity for multimessenger
Astronomy.  Prompt alerts to the Astronomical community will assure that all
available instruments are observing the electromagnetic counterparts to the
first gravitational waves from coalescing compact objects.   Rapid, near
realtime alerts, will improve the chances of detecting weak, decaying
electromagnetic signals and correlating such signals with the gravitational
wave strain.  In this paper, we describe a detection strategy that exploits the
properties of inspiral waveforms using principal component analysis and
multi-rate filtering.  We provide detection efficiency characteristics from a
prototype search pipeline that is capable of \earlywarning\ detection with
acheivable computational requirements.  
\end{abstract}

>>>>

% Backup title.
%\title[LLOID]{Method for early-warning detection of compact binary coalescence.}

@@

\address{$^1$ Canadian Institute for Theoretical Astrophysics, Toronto, ON,
Canada}
\address{$^2$  D\'{e}partement de physique, \'{E}cole Normale Sup\'{e}rieure de Cachan, 61
Avenue du Pr\'{e}sident Wilson, 94235 Cachan Cedex, France}
\address{$^3$ LIGO Laboratory - California Institute of Technology, Pasadena,
CA, USA} 
\address{$^4$ Facultat de Física, Universitat de València, E-46100 Burjassot,
Spain} 
\address{$^5$ The University of Texas at Austin, Austin, TX, USA}
\address{$^6$ Perimeter Institute for Theoretical Physics, Waterloo, ON,
Canada} 
\address{$^7$ Department of Physics and Astronomy, Barnard College, Columbia
University, New York, NY 10027, USA} 
\address{$^8$ Albert-Einstein-Institut, Max-Planck-Institut f\"{u}r
Gravitationphysik, Hannover, Germany} 
\address{$^9$ Leibniz Universit\"{a}t Hannover, Hannover, Germany}
\address{$^{10}$ Ryerson University, Toronto, ON, Canada}

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for multimessenger astronomy.  Prompt detection alerts to the astronomical community may make it possible to observe the onset of electromagnetic emission from compact binary coalescence.  We demonstrate a computationally practical analysis strategy that produces early warning triggers even before gravitational radiation from the final merger has arrived at the detectors.  With current rate estimates for the Advanced \textsc{ligo} design configuration, we should detect $\sim$10 sources earlier than 10 seconds before merger in 1 year of livetime.
\end{abstract}
